### 2018-11-21 sections/objects.tex
Implemented CDS comments by Tom LeCompte, Christian Johnson, and Jason Nielsen

The missing transverse momentum $\mpt$ (with magnitude $\met$) is defined as the negative vector sum of the 
$\pt$ of all selected and calibrated objects in the event, including a term to account for momentum from soft particles 
in the event which are not associated with any of the selected objects. 
This soft term is calculated from inner-detector tracks matched to the selected primary vertex to make it more resilient to
contamination from pile-up interactions~\cite{run_2_met,ATL-PHYS-PUB-2015-027}.

>>>>

The missing transverse momentum $\mpt$ (with magnitude $\met$) is defined as the negative vector sum of the 
$\pt$ of all selected and calibrated objects in the event, including a term to account for momentum from soft particles 
in the event which are not associated with any of the selected objects. 
This soft term is calculated from inner-detector tracks matched to the selected primary vertex to make it more resilient to
contamination from pile-up interactions~\cite{Aaboud:2018tkc}.
